---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(dplyr)
library(here)
read_csv(here("candy.csv"))
```

#1. What is the total number of candy ratings given across the three years. (number of candy ratings, not number of raters. Don’t count missing values)

```{r}
candy %>% summarise(count = sum(!is.na(value)))
```

#2. What was the average age of people who are going out trick or treating and the average age of people not going trick or treating?

```{r}
candy %>% 
  select(age, going_out) %>% 
  filter(going_out == "Yes") %>% 
  summarise(mean(age))

candy %>% 
  select(age, going_out) %>% 
  filter(going_out == "No") %>% 
  summarise(mean(age))
```
#3. For each of joy, despair and meh, which candy bar received the most of these ratings?
```{r}
candy %>%
  select(candy_type, value) %>% 
  filter(value == "JOY") %>% 
  count(candy_type) %>% 
  arrange(desc(value)) %>% 
  slice(1)
  
candy %>% 
  select(candy_type, value) %>% 
  filter(value == "DESPAIR") %>% 
  count(candy_type) %>% 
  arrange(desc(value)) %>% 
  slice(1)

candy %>% 
  select(candy_type, value) %>% 
  filter(value == "MEH") %>% 
  count(candy_type) %>% 
  arrange(desc(value)) %>% 
  slice(1)
```

#4. How many people rated Starburst as despair?
```{r}
candy %>% 
  filter(value == "DESPAIR")
```

#For the next three questions, count despair as -1, joy as +1 and meh as 0.
```{r}
candy <- candy %>% revalue(value, c("DESPAIR" = -1))
revalue(candy$value, c("JOY" = 1)) %>% 
revalue(candy$value, c("MEH" = 0))
```

#5. What was the most popular candy bar by this rating system for each gender in the dataset?
```{r}
candy %>% 
  select(value, candy_type, gender) %>% 
  group_by(gender)
```


#6. What was the most popular candy bar in each year?

#7. What was the most popular candy bar by this rating for people in US, Canada, UK and all other countries?